### 2017-05-06 manuscript/usses_water_ms.Rmd
adds more to methods

### Data Collection
#### Aboveground Net Primary Productivity
We estimated aboveground net primary productivity (ANPP) using a radiometer to related ground reflectance to plant biomass [see @Byrne2011 for a review].

>>>>

### Data Collection
#### Aboveground Net Primary Productivity
We estimated aboveground net primary productivity (ANPP) using a radiometer to relate ground reflectance to plant biomass [see @Byrne2011 for a review].
We recorded ground reflectance at four wavelengths, two associated with red reflectance (xxx and xxx) and two associated with near-infrared reflectance (xxx and xxx).
At each plot in each year, we took four readings of ground reflectances at the above wavelengths.
We also took readings in ten calibration plots adjacent to the experimental site, in which we harvested all aboveground biomass, dried it to a constant weight at 60$^{\circ}$C, and weighed it to estimate ANPP.

For each plot and year, we averaged the four readings for each wavelength and then calculated NDVI using the MODIS and AVHRR algorithms.
To convert NDVI to ANPP we regressed NDVI against the dry biomass weight from the ten calibration plots.
We fit regressions to MODIS-based NDVI and AVHRR-based NDVI for each year and retained the regression with the better fit.
Using the best regression equation for each year, we predicted ANPP.

#### Species Composition
Species composition data came from annual census maps for each plot made using a pantograph [@Hill1920].
The maps record the spatial location and size of each individual plant.
Using those annual maps, we aggregated over individuals to calculate total basal cover for each species in each plot.

### Data Analysis
####  ANPP and Ecosystem Stability

####  Species Synchrony and Species Composition

Results
-------

Discussion
----------

### 2017-05-06 manuscript/usses_water_ms.tex
adds more to methods

We estimated aboveground net primary productivity (ANPP) using a
radiometer to related ground reflectance to plant biomass (see Byrne et
al. 2011 for a review).

@@

>>>>

We estimated aboveground net primary productivity (ANPP) using a
radiometer to relate ground reflectance to plant biomass (see Byrne et
al. 2011 for a review). We recorded ground reflectance at four
wavelengths, two associated with red reflectance (xxx and xxx) and two
associated with near-infrared reflectance (xxx and xxx). At each plot in
each year, we took four readings of ground reflectances at the above
wavelengths. We also took readings in ten calibration plots adjacent to
the experimental site, in which we harvested all aboveground biomass,
dried it to a constant weight at 60\(^{\circ}\)C, and weighed it to
estimate ANPP.

For each plot and year, we averaged the four readings for each
wavelength and then calculated NDVI using the MODIS and AVHRR
algorithms. To convert NDVI to ANPP we regressed NDVI against the dry
biomass weight from the ten calibration plots. We fit regressions to
MODIS-based NDVI and AVHRR-based NDVI for each year and retained the
regression with the better fit. Using the best regression equation for
each year, we predicted ANPP.

\paragraph{Species Composition}\label{species-composition}

Species composition data came from annual census maps for each plot made
using a pantograph (Hill 1920). The maps record the spatial location and
size of each individual plant. Using those annual maps, we aggregated
over individuals to calculate total basal cover for each species in each
plot.

\subsubsection{Data Analysis}\label{data-analysis}

\paragraph{ANPP and Ecosystem
Stability}\label{anpp-and-ecosystem-stability}

\paragraph{Species Synchrony and Species
Composition}\label{species-synchrony-and-species-composition}

\subsection{Results}\label{results}

\subsection{Discussion}\label{discussion}

@@

\hypertarget{ref-Hill1920}{}
Hill, R.R. (1920). Charting Quadrats with a Pantograph. \emph{Ecology},
1, 270--273.
